Stack Safety as a Security Property

### 2020-07-06 main.tex

\definition{Transition} Given a trace $MP$, a call map $\callmap$ and
a code map $\codemap$, an $n$-{\em transition} a pair of
machine-policy state pairs $(\mach_c, \pol_c)$ and $(\mach_e, \pol_e)$
in the trace such that:
\begin{itemize}
\item one state pair steps to the other:
  $$\exists \obs. ~ (\mach_c, \pol_c) \stepstoobs{\obs}_P (\mach_e, \pol_e),$$
\item $\mach_c$ is a valid call with $n$ arguments:
  $$\callmap(\mach_c(\PCname)) = n,$$
\item and $\mach_e$ is an entry point for $f$:
  $$\codemap(\mach_e(\PCname)) = f.$$
\end{itemize}

\definition{Stack Integrity} Let $\callmap$ be a call map and
$\codemap$ a code map. We say that a system satisfies {\em stack
  integrity} with respect to $\callmap$ and $\codemap$ if, for every
initial machine-policy state pair $(\mach_0, \pol_0)$ and its induced
trace $\MPT$, and every $n$-transition $(\mach_c, \pol_c)$ and
$(\mach_e, \pol_e)$ in $MP$, the prefix $\MPT_{pre}$ of $\MPT$ from
$(\mach_e, \pol_e)$ until the first return corresponding to $\mach_c$
(if any) satisfies trace integrity with respect to the contour at the
call:
%
$$\forall \MPT_{pre}. ~ \mpstate{\mach_e}{\pol_e} \hookrightarrow_P
\MPT_{pre} ~ | ~ \ret{\mach_c} \rightarrow
\mathit{int}~\mathit{Cof}(\mach_c, n)~\MPT_{pre}$$

@@

The rest of \Cref{fig:confex1} shows an example that fails \leo{number
  items?  observations of trace?}  \Cref{fig:confex2} shows the
initial states \(\mach_e\), left, and \(\mach_e'\), right. Low
confidentiality data in \fcallc is shared between them, while high
confidentiality data in red and \gprivc may differ.  After executing
the code shown, the final states below have written different values
to address 42, represented by the black and white components.  It is
allowed for address 40 to differ between the states due to the initial
variation, but address 42 changed differently between the traces,
representing a leak of data. %Meanwhile \ref{fig:lazyex2}, while high
confidentiality data
%is read, it is overwritten before return, and the write at step 3 always writes
%the same value. \Gprivc and red locations differ between variations only because
%of the initial variation, and the rest are identical. So this example passes.
\Cref{fig:confex2} gives an example of a trace that fails trace
confidentiality. At instruction 42, {\tt h} reads {\tt x} from {\tt main}.
Since {\tt x}, at address 100, is high confidentiality (red) the variant
may have a different value (\gprivc). So both \(r_4\) and address 107
differ in the final state between the original trace and the variant one,
failing the ending condition of trace confidentiality.

@@

>>>>

\definition{Transition} Given a trace $\MPT$, a call map $\callmap$ and
a code map $\codemap$, an $n$-{\em transition} a pair of
machine-policy state pairs $(\mach_c, \pol_c)$ and $(\mach_e, \pol_e)$
in the trace such that:
\begin{itemize}
\item one state pair steps to the other:
  $$\exists \obs. ~ (\mach_c, \pol_c) \stepstoobs{\obs}_P (\mach_e, \pol_e),$$
\item $\mach_c$ is a valid call with $n$ arguments:
  $$\callmap(\mach_c(\PCname)) = n,$$
\item and $\mach_e$ is an entry point for $f$:
  $$\codemap(\mach_e(\PCname)) = f.$$
\end{itemize}

\definition{Stack Integrity} Let $\callmap$ be a call map and
$\codemap$ a code map. We say that a system satisfies {\em stack
  integrity} with respect to $\callmap$ and $\codemap$ if, for every
initial machine-policy state pair $(\mach_0, \pol_0)$ and its induced
trace $\MPT$, and every $n$-transition $(\mach_c, \pol_c)$ and
$(\mach_e, \pol_e)$ in $\MPT$, the prefix $\MPT_{pre}$ of $\MPT$ from
$(\mach_e, \pol_e)$ until the first return corresponding to $\mach_c$
(if any) satisfies trace integrity with respect to the contour at the
call:
%
$$\forall \MPT_{pre}. ~ \mpstate{\mach_e}{\pol_e} \hookrightarrow_P
\MPT_{pre} ~ | ~ \ret{\mach_c} \rightarrow
\mathit{int}~\mathit{Cof}(\mach_c, n)~\MPT_{pre}$$

@@

For example, consider the unsafe substitution:
\[
42 : ~ \sw ~ r_4 ~ \rsp 100
\]
Instead of reading the proper argument, {\tt h} reads directly from the
secret value of {\tt x} that belongs to {\tt main}. \Cref{fig:confex}
shows \(\mach_e\), the entry state of {\tt h}, with high confidentiality memory
in red and low confidentiality in green. Below it, the variant state
\(\mach_e'\) agrees on low confidentiality memory, but the rest might have
any value, in yellow. After the last step, the return states \(\mach_r\) and
\(\mach_r'\) should agree on every component that changed since \(\mach_e\) or
\(\mach_e'\). Addresses 108 and 109 have changed, shown in pink, and while 109
is consistent, 108 will not hold 43 in all variants, so the trace does not obey
trace confidentiality.

Meanwhile, the following unsafe substitution outputs the secret
directly, violating the internal observation clause of confidentiality:
\[
30 : ~ \lw ~ r_5 ~ \rsp ~ \negate 6
\]
%\Cref{fig:confex2} shows the initial states \(\mach_e\), above,
%and \(\mach_e'\), below. Low confidentiality data in green is shared
%between them, while high confidentiality data in red and yellow may differ.
%After executing the code shown, the final states below have written different
%values to address 42, represented by the black and white components.
%It is allowed for address 40 to differ between the states due to the initial
%variation, but address 42 changed differently between the traces, representing
%a leak of data. %Meanwhile \ref{fig:lazyex2}, while high confidentiality data
%is read, it is overwritten before return, and the write at step 3 always writes
%the same value. \Gprivc and red locations differ between variations only because
%of the initial variation, and the rest are identical. So this example passes.

%\begin{figure}
%  \confidentialityduringexample
%  \caption{Failing Trace Confidentiality by Varying Observations}
%  \label{fig:confex1}
%\end{figure}

\begin{figure}
  \confidentialityendexample
  \caption{Failing Trace Confidentiality}
  \label{fig:confex}
\end{figure}

%\Cref{fig:confex2} gives an example of a trace that fails trace
%confidentiality. At instruction 42, {\tt h} reads {\tt x} from {\tt main}.
%Since {\tt x}, at address 100, is high confidentiality (red) the variant
%may have a different value (yellow). So both \(r_4\) and address 107
%differ in the final state between the original trace and the variant one,
%failing the ending condition of trace confidentiality.

@@

    \begin{figure}
      \integritylazyexample
      \caption{Rolling back from Figure \ref{fig:intex}}
      \label{fig:intlex}
    \end{figure}

    For out example, we return to the violation of trace integrity in
    \cref{fig:intex}, in which {\tt h} has written to {\tt z} and returned.
    Whether observable integrity holds depends on the continuing trace, shown
    in \cref{fig:intlex}. Above, we have the final state of \(\MPT\),
    \(\mach_r\), with high integrity components in red and low integrity in
    green. Next is the rolled-back state, \(\mach_r' =
    \mathit{roll}(\contour,\mach_e,\mach_r)\), in which high integrity
    components are restored to their value as of \(\mach_e\). Specifically,
    address 103 is restored to 0. When instruction 31 prints {\tt z} in the
    trace from \(\mach_r\), it prints 18, but in the trace from \(\mach_r'\)
    it prints 0. So observable trace integrity does not hold.

    However, if {\tt g} had an additional instruction to overwrite {\tt z}
    before printing, observable trace integrity would hold.
